Processing of visual and non-visual naturalistic spatial information in the "parahippocampal place area"

### 2021-02-15 paper/main.tex
results + PPA discussion: honing & typos

% previous studies
Previous studies reported increased hemodynamic activity in the PPA when
participants were watching static pictures of landscape compared to pictures of
faces or objects (e.g. \citep{epstein1998ppa, epstein1999parahippocampal})
whereas one study using spoken sentences reported mixed results
\citep{aziz2008modulation}.
% current study: similar
In line with previous studies, we operationalized spatial perception via general
linear model (GLM) $t$-contrasts.
% current study: dissimilar
Contrary to previous studies, our current approach is not based on carefully
designed sets of stimuli but based on annotated stimulus features incidentally
occurring in two naturalistic stimuli.
% group AV
On a group level, whole brain-analysis results for the movie stimulus show
significantly increased hemodynamic activity spatially overlapping with a
traditionally localized PPA but also extending into earlier visual cortices.
% group AD
Results for the audio-description also reveal significant activation in the PPA
but restricted to its anterior part.
% individual level
On an individual level, results of the audio-description show significant
bilateral clusters in the anterior PPA of nine subjects and significant
unilateral clusters in one subjects.
% meaning: generalization to naturalistic stimuli
Results suggest that increased activation in the PPA during the perception of
static pictures generalizes to the perception of spatial information embedded in
a movie and an exclusively auditory stimulus.
% meaning: aPPA vs. pPPA
Our results provide further evidence that the PPA can be divided into functional
subregions.
% narrative as substitute
An auditory narrative might substitute a visual paradigm to localize
the PPAs anterior part in visually impaired subjects.

\subsection{PPA (group + individuals \& aPPA vs. pPPA)}

% intro
First, we analyzed data from the movie stimulus offering ecologically more valid
but still visual stimulation.
%
An early study \citep{bartels2004mapping} that manually annotated the content of
movie frames (color, faces, language, and human bodies) found that
specialization of functional areas is preserved during movie watching.
%
Contrary to \citep{bartels2004mapping} who annotated the content of frames, we
categorized each frame after a cut independent of its specific content.
\todo{Bartels' clusters are actually pretty big too}
% exploited cinematographic tendencies
We here exploited a cinematographic confound in the stimulus structure (cf.
\ref{rationale}):
% establishing shots vs. e.g. over-the-shoulder shots
film directors tend to establish the geometry of locations earlier in the movie
and tend to later focus more on persons and objects relevant to the evolved
\citep{brown2012cinematography, mercado2011filmmakers}.
% hypo
Despite our ad hoc approach, we hypothesized that confounding variables would
average out, and our whole-brain analyses would lead to significant clusters in
the PPA.
% results
Group results of the AV stimulus' primary contrast yielded one cluster that
spans the group overlap of individual PPA ROIs from anterior to posterior.
% confound of higher perception
The cluster's extension into more posterior, early visual areas can be
attributed to the averaging process that did not control for confounding visual
features.
% solution
Thus to control confounding variables, future studies that aim to use a movie to
localize visual areas should extensively annotate the content of frames (e.g.
using the open-source solution ``Pliers'' for feature extraction from a visual
naturalistic stimulus; \citep{mcnamara2017developing}).
% we took advantage of cinematography
We here took advantage of an idiosyncrasy of movie directing to shift from
establishing the geometry earlier in the movie to later depicting persons and
objects more relevant to the evolved plot.
% know your stimulus
Given that this shift is common in movies, investigators should be aware that
cinematographic tendencies are part of movie's confound structure that might,
depending on the research question, influence the results.
% conclusion
In summary, results from the visual localizer paradigm using blocks of pictures
generalize to an ad hoc approach to operationalize the perception of spatial
information at the moment of cuts in a audio-visual movie.

% intro
Second, we analyzed data from the audio-description offering exclusively
auditory stimulation.
% hypothesis
Encouraged by \citep{aziz2008modulation}, we hypothesized that spatial
information embedded in the AD stimulus would correlate with increased
hemodynamic activity in the PPA.
% diff to Aziz (2008)
\citep{aziz2008modulation} modeled events from on- to offset of sentences
(describing unknown and famous places and faces), and compared activity levels
that were averaged across voxels of ROIs (PPA and fusiform face area, FFA
\citep{kanwisher1997ffa}) defined by a localizer experiment.
% Aziz results
Study results revealed significantly decreased activity in only the left PPA
compared to activity in the FFA for sentences describing famous places compared
to famous faces.
% we: model & whole brain
Here we modeled events from on- to offset of single words and performed a
whole-brain analysis.
% our results
Group results of audio-description's primary contrast yielded spatially concise
clusters in the anterior part of the PPA group overlap.
% concluding statement
Contrary to \citep{aziz2008modulation}, our group results suggest that auditory
spatial information compared to non-spatial information correlates with
bilaterally increased activation in the anterior part of the PPA.

% previous studies: no task
Usually studies that use small sets of experimentally controlled stimuli also
employ a task to keep subjects attentive to the stimuli.
% but: Epstein (1998)
Nevertheless, one early block-design study \citep{epstein1998ppa} compared
results from a paradigm that employed a (perceptual) judgment task of static
pictures to the same paradigm but without that task.
% results during no task
Hemodynamic activity was less but still significantly increased when
participants had no task to keep them alert and attentive to the stimuli.
% we have no task neither
Our paradigm is similar in that sense that our participants had no behavioral or
cognitive task (e.g. forming a mental image of the stimuli; cf.
\citep{ocraven2000mental})  but just had to ``enjoy the audio-description''.
% but still: we are different
Our paradigm still differs from \citep{epstein1998ppa} because the modeled
stimulus features were incidentally embedded in a continuous stream of auditory
information preventing participants from making assumptions about the
investigated perceptual process.
% concluding statement: kinda automatic process
Hence, current results from our paradigm also suggest that verbal spatial
information is processed in the anterior PPA casually and does not [necessarily]
rely on [deliberately] paying attention to verbal spatial information.

@@

% optimal stimulus type in vision
In the visual domain, pictures of landscapes and not pictures of landmarks or
buildings are considered to be the ``optimal'' stimulus type
\citep{epstein2008parahippocampal}.
% we did not choose se\_new and se\_old
In the AD's primary contrast, we did not include the categories that contained
switches from one setting to another (\texttt{se\_new} and \texttt{se\_old})
which one might assume to contain the auditory equivalent to pictures of
landscapes.
% why
The reason was that the categories \texttt{se\_new} and \texttt{se\_old} were
heterogeneous: they rarely contained holistic (but also vague) descriptions of
landscapes (e.g.  ``[Forrest is running through the] jungle'') but mostly
landmarks or buildings, and also non-spatial hints (e.g. ``[Jenny as a]
teenager``).
% further studies
Given that humans can identify the gist of a rich visual scene within the
duration of a single fixation \citep{henderson2003human} further studies might
investigate if vague verbal descriptions of landscapes lead to a different
hemodynamic activity level than descriptions of more concrete parts of a scene
(e.g.``[a] beacon'', [a] ``farmhouse'').

% AD annotation > AV annotation
Given that the annotation of nouns offered a more precise way to operationalize
the perception of spatial information than the annotation of cuts and locations,
we also hypothesized that analyzing the data from the audio-description could
localize the PPA in individual persons.
% results of dedicated localizer
The visual localizer \citep{sengupta2016extension} revealed bilateral ROIs in 12
of 14 subjects and a unilateral right ROI in two subjects (sub-04, sub-20).
%
Whereas \citep{sengupta2016extension} chose the subjectively ``best fitting''
$t$-threshold in an unthresholded $t$-map from one of three contrasts by visual
judgment, we used the same contrast and threshold (Z>3.4, p<.05
cluster-corrected) for all subjects.
% in the current study
The audio-description yielded significant bilateral clusters in 9 of 14 subjects
(of which sub-04 shows only a right-lateralized PPA ROI), and a unilateral
significant cluster in one subject.
% similar: anterior part
Similarly to the group average results, results on an individual level also
revealed that clusters are spatially restricted to the anterior part of
individual PPAs.
% conclusion
Thus, the cluster location and size found on the group level is not just a
by-product of the averaging process but a reliable pattern across results of
individual study participants.
% concluding statement
Further, our exploratory analysis suggests that a naturalistic auditory stimulus
can [in principle] be applied to localize (the anterior part) of an higher-level
visual area in the majority of subjects.
% one threshold (and contrast) to rule them all
Nevertheless, further studies that aim for individual diagnostics / ROI
localization should inspect more than one contrast, and use an individual
threshold or a sphere around the local maximum \citep{poldrack2007region} in the
parahippocampal region.

@@

% question
The fact that clusters from the auditory stimulus are spatially restricted to
the anterior part of clusters from the visual paradigms raises the question if
the revealed correlation patterns can be attributed to different features
inherent in the visual compared to the verbal stimuli.
% visual scenes: probably submodules
In the domain of visual scene perception, previous studies provide evidence that
the PPA can be divided into functionally subregions that might process different
stimulus features.
% posterior: functionality
The posterior PPA (pPPA) is functionally more responsive than the anterior PPA
(aPPA) to low-level features of scenes or (abstract) objects
\citep{baldassano2013differential, nasr2014thinking,
rajimehr2011parahippocampal}.
% anterior cIPL is defined using the Eickhoff–Zilles PGp probabilistic
% cytoarchitectonic map
Contrary, the aPPA is functionally more responsive than the pPPA to high-level
features of scenes (e.g. real-word size \citep{park2015parametric}; a scene's
abstract identity/category \citep{marchette2015outside, watson2016patterns}) and
objects (e.g. spatial contextual associations \citep{aminoff2007parahippocampal,
aminoff2013role}).
% connectivity
Moreover, pPPA and aPPA show differences in connectivity profiles.
% posterior
The pPPA is more strongly functionally connected to the occipital visual cortex
than the aPPA \citep{baldassano2013differential, baldassano2016two}.
% including lateral occipital cortex (LOC) and transverse occipital sulcus (TOS)
% anterior
Contrary, the aPPA is more strongly functionally connected to portions of the
default mode network, including caudal inferior parietal lobe (cIPL), the
restrosplenial complex (RSC), medial PFC and the lateral surface of the anterior
temporal lobe \citep{baldassano2013differential, baldassano2016two}.
% conclusion: subregions
According to the hypothesis by \citep{baldassano2013differential} the PPA
consists of subregions that process specific apsects of a visual scene and
cooperate to build a complete scene representation.
% Their distinct connectivity properties do suggest that each may be involved in
% specific aspects of visual and cognitive processing involved in the
% overarching goal of scene understanding \citep{baldassano2013differential}.
% The fact that anterior PPA had a lower sensitivity to our abstract object
% stimuli does not necessarily imply that this region does not use object
% information \citep{baldassano2013differential}. Previous work has shown that
% PPA responds to objects that have spatial associations [Aminoff et al. 2007],
% are space-defining [Mullally and Maguire 2011], and are
% navigationally-relevant [Janzen and Van Turennout 2004]. These types of
% responses require spatial memory and cannot be based purely on visual features
% like object shape. \citep{baldassano2013differential}.
Our results add further evidence that the PPA is not a homogeneous area but can
be divided into functionally subregions.
% pPPA
Our results suggest that the pPPA is more concerned with visual aspects immanent
in pictures or movie shots of landscapes.
% aPPA
The aPPA might be more concerned with non-visual aspects of spatial information
(e.g. spatial contextual information \citep{aminoff2013role,
aminoff2015associative, baumann2016functional}) as inherent in both visual and
verbal stimuli.

\subsection{RSC \& LOC; naturalistic stimuli}

% intro
Apart from the PPA, we find significantly increased activity in the dorsal
precuneus and posterior cingulate region (e.g. retrosplenial complex; RSC) and
lateral occipital cortex (LOC; more lateral in the AV stimulus, more medial in
the AD stimulus) across contrasts of both naturalistic stimuli.
% RSC intro
Like the PPA, the RSC and LOC repeatedly showed increased hemodynamic activity
in studies investigating visual spatial perception or navigation (see
\citep{chrastil2018heterogeneity, bettencourt2013role} for reviews).
% not random shit
Thus, our approach to operationalize spatial perception based on stimulus
annotations did not lead to significant clusters scattered across the brain but
restricted to a brain network that is assumed/known to be involved in (visual)
spatial perception and cognition.
%
This suggest that model-driven methods based on stimulus annotations are
suitable to reveal spatially concise functional areas and networks.
%
Nevertheless, ``cleanliness''/``neatness``  of results (i.e. the signal-cluster
to noise-cluster ration)\todo{if you know what I mean} depends on how many
events correlating with an assumed perceptual process the stimulus provides
and to the extent to which a naturalistic stimulus' multi-dimensionality is
annotated and statistically controlled.

>>>>

% previous studies
Previous studies reported increased hemodynamic activity in the PPA when
participants were watching static pictures of landscape compared to pictures of
faces or objects (e.g. \citep{epstein1998ppa, epstein1999parahippocampal})
whereas one study using spoken sentences reported mixed results
\citep{aziz2008modulation}.
% current study: similar
In line with previous studies, we operationalized spatial perception via general
linear model (GLM) $t$-contrasts.
% current study: dissimilar
Contrary to previous studies, our current approach is not based on carefully
designed sets of stimuli but based on annotated stimulus features incidentally
occurring in two naturalistic stimuli.
% group AV
On a group level, whole brain-analysis results for the audio-visual movie show
significantly increased hemodynamic activity spatially overlapping with a
traditionally localized PPA but also extending into earlier visual cortices.
% group AD
Results for the audio-description also reveal significant activation in the PPA
but restricted to its anterior part.
% individual level
On an individual level, results of the audio-description show significant
bilateral clusters in the anterior PPA of nine subjects and a unilateral cluster
in one subjects.
% meaning: generalization to naturalistic stimuli
Results suggest that increased activation in the PPA during the perception of
static pictures generalize to the perception of spatial information embedded in
a movie and an exclusively auditory stimulus.
% meaning: aPPA vs. pPPA
Our results provide further evidence that the PPA can be divided into functional
subregions.
% narrative as substitute
An auditory narrative might substitute a visual paradigm to localize the PPAs
anterior part in visually impaired subjects.

% PPA: intro
First, we analyzed data from the movie offering ecologically more valid visual
stimulation.
%
An early study \citep{bartels2004mapping} that manually annotated the content of
movie frames (color, faces, language, and human bodies) found that
specialization of functional areas is preserved during movie watching.
%
Contrary to \citep{bartels2004mapping} who annotated the content of movie
frames, we categorized each frame after a cut independent of its specific
content  \todo{Bartels' clusters are actually pretty big too}
% exploited cinematographic tendencies
exploiting a cinematographic confound in the stimulus structure (cf. section
\ref{rationale}):
% establishing shots vs. e.g. over-the-shoulder shots
film directors tend to establish the geometry of locations earlier in the movie
and tend to later focus more on persons and objects relevant to the evolved plot
\citep{brown2012cinematography, mercado2011filmmakers}.
% hypo
Despite our ad hoc approach, we hypothesized that confounding variables would
average out, and our whole-brain analyses would lead to significant clusters in
the PPA.
% results
Group results of the AV stimulus' primary contrast yielded one cluster that
spans the group overlap of individual PPA ROIs from anterior to posterior.
% confound of higher perception
The cluster's extension into more posterior, early visual areas can be
attributed to the averaging process that did not control for confounding visual
features.
% solution
Thus to control confounding variables, future studies that aim to use a movie to
localize visual areas in individual subjects should extensively annotate the
content of frames (e.g.  using the open-source solution ``Pliers'' for feature
extraction from a visual naturalistic stimulus; \citep{mcnamara2017developing}).
% we took advantage of cinematography
We here took advantage of an idiosyncrasy of movie directing to shift from
depicting the spatial layout to to later depicting persons and objects.
% know your stimulus
Given that this shift is common in movies, investigators should be aware that
cinematographic tendencies are part of movie's confound structure that might,
depending on the research question, influence the results.
% conclusion
In summary, results from the visual localizer paradigm using blocks of pictures
generalize to an ad hoc approach to operationalize the perception of spatial
information at the moment of cuts in an audio-visual movie.

% intro
Second, we analyzed data from the audio-description offering exclusively
auditory stimulation.
% hypothesis
Encouraged by \citep{aziz2008modulation}, we hypothesized that spatial
information embedded in the AD stimulus would correlate with increased
hemodynamic activity in the PPA.
% diff to Aziz (2008)
\citep{aziz2008modulation} modeled events from on- to offset of sentences
(describing unknown and famous places and faces), and compared activity levels
that were averaged across voxels of ROIs (PPA and fusiform face area, FFA
\citep{kanwisher1997ffa}) defined by a localizer experiment.
% Aziz results
Study results revealed significantly decreased activity in only the left PPA
compared to activity in the FFA for sentences describing famous places compared
to famous faces.
% we: model & whole brain
Here we modeled events from on- to offset of single words and performed a
whole-brain analysis.
% our results
Group results of the audio-description's primary contrast yielded significantly
increased hemodynamic activity spatially restricted to the anterior part of the
PPA group overlap.
% concluding statement
Contrary to \citep{aziz2008modulation}, our group results suggest that auditory
spatial information compared to non-spatial information correlates with
bilaterally increased activation in the anterior part of the PPA.

% previous studies: no task
Usually studies that use small sets of experimentally controlled stimuli also
employ a task to keep subjects attentive to the stimuli.
% but: Epstein (1998)
Nevertheless, one early block-design study \citep{epstein1998ppa} compared
results from a paradigm that employed a perceptual judgment task of static
pictures to the same paradigm but without that task.
% results during no task
Hemodynamic activity was less but still significantly increased when
participants had no task to keep them alert and attentive to the stimuli.
% we have no task neither
Our paradigm is similar in that sense that our participants had no behavioral or
cognitive task (e.g. forming a mental image of the stimuli; cf.
\citep{ocraven2000mental})  but just had to ``enjoy the audio-description''.
% but still: we are different
Our paradigm still differs from \citep{epstein1998ppa} because the modeled
stimulus features were incidentally embedded in a continuous stream of auditory
information preventing participants from making assumptions about the
investigated perceptual process.
% concluding statement: kinda automatic process
Hence, current results also suggest that verbal spatial information is processed
in the anterior PPA casually and does not [necessarily] rely on [deliberately]
paying attention to verbal spatial information.

@@

% optimal stimulus type in vision
In the visual domain, pictures of landscapes and not pictures of landmarks or
buildings are considered to be the ``optimal'' stimulus type
\citep{epstein2008parahippocampal}.
% we did not choose se\_new and se\_old
In the AD's primary contrast, we did not include the categories that contained
switches from one setting to another (\texttt{se\_new} and \texttt{se\_old})
which one might assume to contain the auditory equivalent to pictures of
landscapes.
% why
The reason was that the categories \texttt{se\_new} and \texttt{se\_old} were
heterogeneous: they rarely contained holistic (but also vague) descriptions of
landscapes (e.g.  ``[Forrest is running through the] jungle'') but mostly
landmarks or buildings, and also non-spatial hints (e.g. ``[Jenny as a]
teenager``).
% visual system => gist in milliseconds
Humans can identify the gist of a rich visual scene within the duration of a
single fixation \citep{henderson2003human}.
%
Hence, further studies might investigate if vague verbal descriptions of
landscapes lead to a different hemodynamic activity level than descriptions of
more concrete parts of a scene (e.g.``[a] beacon'', [a] ``farmhouse'').

% AD annotation > AV annotation
Given that the annotation of nouns offered a more precise way to operationalize
the perception of spatial information than the annotation of cuts and locations,
we also hypothesized that analyzing the data from the audio-description could
localize the PPA in individual persons.
% results of dedicated localizer
The visual localizer \citep{sengupta2016extension} revealed bilateral ROIs in 12
of 14 subjects and a unilateral right ROI in two subjects (sub-04, sub-20).
%
Whereas \citep{sengupta2016extension} chose the subjectively ``best fitting''
$t$-threshold in $t$-map from one of three contrasts by visual judgment, we used
the same contrast and threshold (Z>3.4, p<.05 cluster-corrected) for all
subjects.
% in the current study
The audio-description yielded significant bilateral clusters in 9 of 14 subjects
(of which sub-04 shows only a right-lateralized PPA ROI), and a unilateral
significant cluster in one subject.
% similar: anterior part
Similarly to the group average results, results on an individual level also
revealed that clusters are spatially restricted to the anterior part of
individual PPAs.
% conclusion
Thus, the cluster location and size found on the group level is not just a
by-product of the averaging process but a reliable pattern across results of
individual study participants.
% concluding statement
Further, our exploratory analysis suggests that a naturalistic auditory stimulus
can [in principle] be applied to localize (the anterior part) of a higher-level
visual area in the majority of subjects.
% one threshold (and contrast) to rule them all
Nevertheless, further studies that aim for individual diagnostics / ROI
localization should inspect more than one contrast, and use an individual
threshold or a sphere around the local maximum \citep{poldrack2007region} in the
parahippocampal region.

@@

% question
The fact that clusters from the auditory stimulus are spatially restricted to
the anterior part of clusters from the visual paradigms raises the question if
the revealed correlation patterns can be attributed to different features
inherent in the visual compared to the verbal stimuli.
% visual scenes: probably submodules
In the domain of visual scene perception, previous studies provide evidence that
the PPA can be divided into functionally subregions that might process different
stimulus features.
% posterior: functionality
The posterior PPA (pPPA) is functionally more responsive than the anterior PPA
(aPPA) to low-level features of scenes or (abstract) objects
\citep{baldassano2013differential, nasr2014thinking,
rajimehr2011parahippocampal}.
% anterior cIPL is defined using the Eickhoff–Zilles PGp probabilistic
% cytoarchitectonic map
Contrary, the aPPA is functionally more responsive than the pPPA to high-level
features of scenes (e.g. real-word size \citep{park2015parametric}; a scene's
abstract identity/category \citep{marchette2015outside, watson2016patterns}) and
objects (e.g. spatial contextual associations \citep{aminoff2007parahippocampal,
aminoff2013role}).
% connectivity
Moreover, pPPA and aPPA show differences in connectivity profiles.
% posterior
The pPPA is more strongly functionally connected to the occipital visual cortex
than the aPPA \citep{baldassano2013differential, baldassano2016two}.
% including lateral occipital cortex (LOC) and transverse occipital sulcus (TOS)
% anterior
Contrary, the aPPA is more strongly functionally connected to portions of the
default mode network[, including caudal inferior parietal lobe (cIPL), the
restrosplenial complex (RSC), medial PFC and the lateral surface of the anterior
temporal lobe] \citep{baldassano2013differential, baldassano2016two}.
% conclusion: subregions
According to a hypothesis by \citep{baldassano2013differential} the PPA consists
of subregions that process different aspects of a visual scene and cooperate to
build a complete scene representation.
% Their distinct connectivity properties do suggest that each may be involved in
% specific aspects of visual and cognitive processing involved in the
% overarching goal of scene understanding \citep{baldassano2013differential}.
% The fact that anterior PPA had a lower sensitivity to our abstract object
% stimuli does not necessarily imply that this region does not use object
% information \citep{baldassano2013differential}. Previous work has shown that
% PPA responds to objects that have spatial associations [Aminoff et al. 2007],
% are space-defining [Mullally and Maguire 2011], and are
% navigationally-relevant [Janzen and Van Turennout 2004]. These types of
% responses require spatial memory and cannot be based purely on visual features
% like object shape. \citep{baldassano2013differential}.  pPPA
Similarly, our results suggest that the pPPA is more concerned with visual
aspects immanent in pictures or movie shots of landscapes.
% aPPA
The aPPA might be more concerned with non-visual aspects of spatial information
(e.g. spatial contextual information \citep{aminoff2013role,
aminoff2015associative, baumann2016functional}) as immanent in both visual and
verbal stimuli.

% RSC + LOC
Apart from the PPA, we find significantly increased activity in the dorsal
precuneus and posterior cingulate region (e.g. retrosplenial complex; RSC) and
lateral occipital cortex (LOC; more lateral in the AV stimulus, more medial in
the AD stimulus) across contrasts of both naturalistic stimuli.
% RSC intro
Like the PPA, the RSC and LOC repeatedly showed increased hemodynamic activity
in studies investigating visual spatial perception or navigation (see
\citep{chrastil2018heterogeneity, bettencourt2013role} for reviews).
% not random shit
Thus, our approach to operationalize spatial perception based on stimulus
annotations did not lead to significant clusters scattered across the brain but
restricted to a brain network that is assumed/known to be involved in (visual)
spatial perception and cognition.
%
This suggest that model-driven methods based on stimulus annotations are
suitable to reveal spatially concise functional areas and networks.
%
Nevertheless, ``cleanliness''/``neatness``  of results (i.e. the signal-cluster
to noise-cluster ration)\todo{if you know what I mean} depends on how many
events correlating with an assumed perceptual process the stimulus provides
and to the extent to which a naturalistic stimulus' multi-dimensionality is
annotated and statistically controlled.
